Higgs Assisted Razor Search for Higgsinos at 100 TeV

### 2019-07-14 main.tex
Removing font-related lines
Removed unicode character
Addressed some comments

\documentclass[a4paper,11pt]{article}
 \providecommand{\tightlist}{%
     \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{graphicx}
\usepackage{jheppub} 
\usepackage{comment} 
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{slashed}
\usepackage{pgfplots}
\usepackage[T1]{fontenc}
\usepackage{fontspec}
\usepackage{booktabs, longtable}
\bibliographystyle{JHEP.bst}

\newcommand{\Shufang}[1]{{\bf\color{Maroon}  #1}}
\newcommand{\Adarsh}[1]{{\bf\color{RoyalBlue} AP: #1}}
\newcommand{\ap}[1]{\textcolor{RoyalBlue}{#1}}
\renewcommand{\H}{\widetilde{H}^0}
\renewcommand{\B}{\widetilde{B}^0}
\newcommand{\N}{\widetilde{\chi}^0}
\newcommand{\image}[2]{\parbox{#1\textwidth}{\includegraphics[width=#1\textwidth]{images/#2.pdf}}}
\newcommand{\met}{{\slashed{E}_T}}

@@

% Why go beyond the MSSM?
Though a natural MSSM spectrum has the potential to tame the hierarchy
problem, it is under siege from recent data from the Large Hadron
Collider (LHC) \cite{Aaboud:2018ujj, Sirunyan:2018vjp}. 
A compelling alternative scenario comes in the form of
split supersymmetry (split SUSY) \citep{Wells:2003tf,
ArkaniHamed:2004yi, Giudice:2004tc}. In this scenario, the lightest
superpartners are the fermionic ones, on the
scale of 1-10 TeV, while the scalar superpartners can be much heavier,
on the scale of 100 - 1000 TeV. In exchange for accepting some level of
fine-tuning, we obtain numerous benefits, including the suppression of
flavor-changing neutral currents and greater compatibility with data
from CP-violation experiments.  The low lying 
fermionic superpartners consist of neutralinos and charginos (collectively known as Electroweakinos), and gluinos. The current LHC search limits on gluinos are already around xxx TeV~\cite{}.  The limits on Electroweakinos, howeer, are still relatively weak: around xxx $-$ xxx GeV~\cite{}, depending on the decay modes of the parent electroweakinos.  \Shufang{add ref for gluno limit and electroweakino limits.  Fill in the number.} In this paper, we will focus on the discovery potential of the neutralinos and charginos at the 100 TeV $pp$ collider.

% Point to review papers for enumeration of studies
The decay patterns of the Electroweakinos (Winos, Binos, and Higgsinos)
depend on the hierarchy of the MSSM parameters $M_1, M_2$, and $|\mu|$, which 
roughly determine the masses of the Bino, Winos, and Higgsinos, respectively.
In this paper, we consider the Higgsino NLSP and Bino LSP scenario with $M_1 < |\mu| \ll M_2$.
One of the motivations for studying Higgsinos is that the parameter $\mu$ 
that governs its mass plays an important role in electroweak symmetry breaking 
\citep{Acharya:2014pua}. Finding Higgsinos has traditionally been more challenging 
than finding Winos, due to their lower production rate. This, however, can 
be remedied by the increased  production cross sections and luminosities 
at a 100 TeV collider.

@@

The neutralino sector of MSSM consists of four mass eigenstates
($\N_1,\N_2,\N_3,\N_4$), which
are mixtures of the Bino, Wino, and two neutral Higgsinos: 
($\B,\widetilde{W}^0,\H_u,\H_d$). In the basis of these gauge eigenstates, the mass
matrix of the neutralinos can be written as

@@

\[\mathbf{M}_{\widetilde{N}}=
\begin{pmatrix}
  M_1 & 0 & -\cb\sw\mz & \sinb\sw\mz \\
  0 & M_2 & \cb\cw\mz & \sinb\cw\mz \\
  -\cb\sw\mz & \cb\cw\mz & 0 & -\mu \\
  \sinb\sw\mz & -\sinb\cw\mz & -\mu & 0
\end{pmatrix},\]
\Shufang{Check.  I think this matrix goes with ($\B,\widetilde{W}^0,\H_d,\H_u$).}
\noindent where we employ the notation $s_W, c_W = \sin\theta_W, \cos\theta_W$ for $\theta_W$ being the Weinberg mixing angle. $s_\beta, c_\beta$ are defined accordingly with $\tan\beta= v_u/v_d$, where $v_u$ and $v_d$ are the
vacuum expectation values of $H_u^0$ and $H_d^0$, with $v_u^2+v_d^2=v^2=(246\ {\rm GeV})^2$. The parameters $M_1$, $M_2$,
and $\mu$ are the mass parameters of Bino, Wino, and Higgsinos.  The mass eigenstates are usually labels as $\chi_i^0$ for $i=1 \ldots 4$ with increasing mass eigenvalues.

@@

The optimal search strategy for finding Electroweakinos is highly dependent on
the their mass spectrums \citep{Han:2013kza}.   Phenomenological collider studies on finding
Electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a 100 TeV collider can be
found in \citep{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa},
\Shufang{Say a few words about typical search strategy there.}.
Well-separated spectra have been studied in \citep{Gori:2014oua,
Acharya:2014pua} using
multi-lepton channels, of the form 
\begin{equation}
pp\rightarrow \widetilde{\chi}_i\widetilde{\chi}_j\rightarrow VV +
\widetilde{\chi}_1^0\widetilde{\chi}_1^0\rightarrow 2l/3l +  
\met,
\end{equation}
\noindent where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino, and
$\widetilde{\chi}_1^0$ is the lightest neutralino. These searches work well since
the large mass difference between the Electroweakinos can lead to energetic
leptons that can be easily identified. Among the multi-lepton searches for
Higgsinos, the trilepton searches: $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm\rightarrow WZ\widetilde\chi_1^0\widetilde\chi_1^0\rightarrow \ell\ell\ell + \met$ have the best reach, due to the relatively high production cross-section of
chargino-neutralino pairs combined with the large reduction in $t\overline{t}$
and QCD backgrounds obtained by requiring three leptons.   The cross sections for trilepton process can be find in Table~\ref{tab:xsections}. Multilepton searches
with \emph{Zh} and \emph{ZZ} as the intermediate dibosons are unlikely to be as powerful,
due to the lower pair-production cross-section of neutral Higgsinos, combined
with the low branching ratio of \emph{Z/h} to leptons. However, if we move beyond
multilepton searches, the channel with \emph{Zh} (originally suggested in
\citep{Han:2013kza}) as the intermediate dibosons emerges as a possible
competitor to the \emph{WZ} channel.

\begin{table}
  \centering
  \begin{tabular}{l|rr}
    \toprule
    Stage & $\N_{2,3}\widetilde{\chi}^\pm_{2}$ & $\N_2\N_3$\\
    \midrule
    Pair production cross section & 60 fb & 16 fb\\
    Intermediate diboson contribution & ($WZ$) 30 fb  & ($Zh$) 8 fb \\
    Applying \emph{BR}$(W\rightarrow l\nu)$, \emph{BR}$(Z\rightarrow ll)$ \& \emph{BR}$(h\rightarrow bb)$ & 0.42 fb & 0.32 fb\\
    \bottomrule
  \end{tabular}
  \caption{Comparison of cross-sections for
    $(\widetilde{\chi}_{2,3}^0\widetilde{\chi}^\pm_{2})$ and
    $(\N_{2}\N_{3})$, for $|\mu|\approx 1$ TeV, at a 100
    TeV \emph{pp} collider. The pair-production cross sections are taken from
    \citep{Gori:2014oua}. The branching ratio to intermediate dibosons is
    evaluated in the limit where the Goldstone equivalence theorem applies, so
    that BR$(\widetilde{\chi}_{2,3}^0\rightarrow\widetilde{\chi}_{1}^0)\approx$
    BR$(\widetilde{\chi}_{2,3}^0\rightarrow\widetilde{\chi}_1^0)\approx 50\% $,
    and the branching ratios to the SM final states are taken from
    \citep{Olive:2016xmw}.  \Shufang{Specify M1 as well and use the actual Br.} \Shufang{rewrite the entry.  Why chi2pm? Should not it be chi1pm?}}
  \label{tab:xsections}
\end{table}

@@

In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production cross section for the Higgsino-like NLSPs.  The cross section varies between 200 fb to 0.5 fb for Higgsino masses between 500 GeV and 2500 GeV. The right panel of Fig.~\ref{fig:xsection_plot} shows the decay branching fractions of $\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as cauculated in SUSY-HIT. \Shufang{Add ref for SUSYHIT.}  While one of the Higgsinos mostly decays to $Z$, the other Higgsino mostly decays to $h$.  $Zh+\met$ signal thus provide an alternative discovery channel for Higgsinos.

@@

Searches for pair produced nearly mass-degenerate Higgsinos  have been performed 
at ATLAS and CMS for various decay  topologies. While the identity of the 
LSP in these searches is a gravitino  instead of a Bino,   the limits are still  relevant, since both  our analysis  and the experimental ones consider that  
the neutral Higgsinos decay to a  neutral SM boson (\emph{h/Z})  and the 
LSP 100\% of the time.  \Shufang{But this is not the same as our Higgsino NLSP and Bino LSP case.}

@@

  \item \emph{Razor variables}:  Two razor variables are used in our analyses: 
\begin{eqnarray}
M_R &=& \sqrt{(E_Z+E_h)^2 - (p_Z^z + p_h^z)^2},\\ M_T^R &=& \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)^2 - \vec{\slashed{E}}_T\cdot(\vec{p}_{ZT}+\vec{p}_{hT})\right]}，
\end{eqnarray} 
 for$E_{Z,h}$ and $p_{Z,h}$ being the reconstructed energy and momentum for $Z$ and $h$.
\Shufang{Check the formula.  Unit is not correct.}
    Representative kinematic
  distributions of these variables for signal events of a 1 TeV Higgsino and a 25 GeV Bino, as well as $tt$ and $tbW$ backgrounds are
  shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification, and
  $\slashed{E}_{T}$ cuts. The
  distribution for the \emph{bbWW} background is not shown, since it is negligible in
  comparison to the others.   We can see that the distribution of $M_R$ is peaked
  around 1 TeV for the signal, which consistent with what we would expect, since
  it corresponds to the mass difference between the NLSP and LSP.  For this mass combination, requiring $M_R >$ 800
  GeV and $M_T^R >$ 400 GeV yields the greatest significance.

>>>>

\documentclass[a4paper,11pt]{article}
 \providecommand{\tightlist}{%
     \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{graphicx}
\usepackage{jheppub} 
\usepackage{comment} 
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{slashed}
\usepackage{pgfplots}
\usepackage{booktabs, longtable}
\bibliographystyle{JHEP.bst}

\newcommand{\Shufang}[1]{{\bf\color{Maroon}  #1}}
\newcommand{\Adarsh}[1]{{\bf\color{RoyalBlue} AP: #1}}
\newcommand{\ap}[1]{\textcolor{RoyalBlue}{#1}}
\renewcommand{\H}{\widetilde{H}^0}
\newcommand{\B}{\widetilde{B}^0}
\newcommand{\N}{\widetilde{\chi}^0}
\newcommand{\image}[2]{\parbox{#1\textwidth}{\includegraphics[width=#1\textwidth]{images/#2.pdf}}}
\newcommand{\met}{{\slashed{E}_T}}

@@

% Why go beyond the MSSM?
Though a natural MSSM spectrum has the potential to tame the hierarchy
problem, it is under siege from recent data from the Large Hadron
Collider (LHC) \cite{Aaboud:2018ujj, Sirunyan:2018vjp}. 
A compelling alternative scenario comes in the form of
split supersymmetry (split SUSY) \citep{Wells:2003tf,
ArkaniHamed:2004yi, Giudice:2004tc}. In this scenario, the lightest
superpartners are the fermionic ones, on the
scale of 1-10 TeV, while the scalar superpartners can be much heavier,
on the scale of 100 - 1000 TeV. In exchange for accepting some level of
fine-tuning, we obtain numerous benefits, including the suppression of
flavor-changing neutral currents and greater compatibility with data
from CP-violation experiments.  The low lying 
fermionic superpartners consist of neutralinos and charginos (collectively
known as electroweakinos), and gluinos. The current LHC search limits on
gluinos are already around 2.4 TeV~\cite{CMS-PAS-SUS-19-005}. \Adarsh{Should
2460 GeV be rounded up to 2.5 TeV or down to 2.4 TeV to be conservative? Also,
this limit is from the disappearing track search - does that apply for us?} The
limits on electroweakinos,
howeer, are still relatively weak: around xxx $-$ xxx GeV~\cite{}, depending on
the decay modes of the parent electroweakinos.  \Shufang{add ref for 
electroweakino limits. Fill in the number.} In this paper, we will
focus on the discovery potential of the neutralinos and charginos at the 100
TeV $pp$ collider.

% Point to review papers for enumeration of studies
The decay patterns of the electroweakinos (Winos, Binos, and Higgsinos)
depend on the hierarchy of the MSSM parameters $M_1, M_2$, and $|\mu|$, which 
roughly determine the masses of the Bino, Winos, and Higgsinos, respectively.
In this paper, we consider the Higgsino NLSP and Bino LSP scenario with $M_1 < |\mu| \ll M_2$.
One of the motivations for studying Higgsinos is that the parameter $\mu$ 
that governs its mass plays an important role in electroweak symmetry breaking 
\citep{Acharya:2014pua}. Finding Higgsinos has traditionally been more challenging 
than finding Winos, due to their lower production rate. This, however, can 
be remedied by the increased  production cross sections and luminosities 
at a 100 TeV collider.

@@

The neutralino sector of MSSM consists of four mass eigenstates
($\N_1,\N_2,\N_3,\N_4$), which
are mixtures of the Bino, Wino, and two neutral Higgsinos: 
($\B,\widetilde{W}^0,\H_d,\H_u$). In the basis of these gauge eigenstates, the mass
matrix of the neutralinos can be written as

@@

\[\mathbf{M}_{\widetilde{N}}=
\begin{pmatrix}
  M_1 & 0 & -\cb\sw\mz & \sinb\sw\mz \\
  0 & M_2 & \cb\cw\mz & -\sinb\cw\mz \\
  -\cb\sw\mz & \cb\cw\mz & 0 & -\mu \\
  \sinb\sw\mz & -\sinb\cw\mz & -\mu & 0
\end{pmatrix},\]

\Shufang{Check.  I think this matrix goes with
($\B,\widetilde{W}^0,\H_d,\H_u$). \Adarsh{Good catch - I have fixed it.}}
\noindent where we employ the notation $s_W, c_W = \sin\theta_W, \cos\theta_W$
for $\theta_W$ being the Weinberg mixing angle. $s_\beta, c_\beta$ are defined
accordingly with $\tan\beta= v_u/v_d$, where $v_u$ and $v_d$ are the vacuum
expectation values of $H_u^0$ and $H_d^0$, with $v_u^2+v_d^2=v^2=(246\ {\rm
GeV})^2$. The parameters $M_1$, $M_2$, and $\mu$ are the mass parameters of
Bino, Wino, and Higgsinos.  The mass eigenstates are usually labels as
$\chi_i^0$ for $i=1 \ldots 4$ with increasing mass eigenvalues.

@@

The optimal search strategy for finding electroweakinos is highly dependent on
the their mass spectrums \citep{Han:2013kza}.  Phenomenological collider studies on finding
Electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a 100 TeV collider can be
found in \citep{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa},
\Shufang{Say a few words about typical search strategy there.} \Adarsh{I
believe I've already addressed this with the paragraphs I added below in response
to your comment ... let me know if I should add more details.}.
Well-separated spectra have been studied in \citep{Gori:2014oua,
Acharya:2014pua} using
multi-lepton channels, of the form 
\begin{equation}
pp\rightarrow \widetilde{\chi}_i\widetilde{\chi}_j\rightarrow VV +
\widetilde{\chi}_1^0\widetilde{\chi}_1^0\rightarrow 2l/3l +  
\met,
\end{equation}
\noindent where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino, and
$\widetilde{\chi}_1^0$ is the lightest neutralino. These searches work well since
the large mass difference between the Electroweakinos can lead to energetic
leptons that can be easily identified. Among the multi-lepton searches for
Higgsinos, the trilepton searches: $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm\rightarrow WZ\widetilde\chi_1^0\widetilde\chi_1^0\rightarrow \ell\ell\ell + \met$ have the best reach, due to the relatively high production cross-section of
chargino-neutralino pairs combined with the large reduction in $t\overline{t}$
and QCD backgrounds obtained by requiring three leptons.   The cross sections for trilepton process can be find in Table~\ref{tab:xsections}. Multilepton searches
with \emph{Zh} and \emph{ZZ} as the intermediate dibosons are unlikely to be as powerful,
due to the lower pair-production cross-section of neutral Higgsinos, combined
with the low branching ratio of \emph{Z/h} to leptons. However, if we move beyond
multilepton searches, the channel with \emph{Zh} (originally suggested in
\citep{Han:2013kza}) as the intermediate dibosons emerges as a possible
competitor to the \emph{WZ} channel.

\begin{table}
  \centering
  \begin{tabular}{l|rr}
    \toprule
    Stage & $\N_{2,3}\widetilde{\chi}^\pm_{2}$ & $\N_2\N_3$\\
    \midrule
    Pair production cross section & 60 fb & 16 fb\\
    Intermediate diboson contribution & ($WZ$) 30 fb  & ($Zh$) 8 fb \\
    Applying \emph{BR}$(W\rightarrow l\nu)$, \emph{BR}$(Z\rightarrow ll)$ \& \emph{BR}$(h\rightarrow bb)$ & 0.42 fb & 0.32 fb\\
    \bottomrule
  \end{tabular}
  \caption{Comparison of cross-sections for
    $(\widetilde{\chi}_{2,3}^0\widetilde{\chi}^\pm_{2})$ and
    $(\N_{2}\N_{3})$, for $|\mu|\approx 1$ TeV, at a 100
    TeV \emph{pp} collider . The pair-production cross sections are taken from
    \citep{Gori:2014oua}. The branching ratio to intermediate dibosons is
    evaluated in the limit where the Goldstone equivalence theorem applies, so
    that BR$(\widetilde{\chi}_{2,3}^0\rightarrow\widetilde{\chi}_{1}^0)\approx$
    BR$(\widetilde{\chi}_{2,3}^0\rightarrow\widetilde{\chi}_1^0)\approx 50\% $,
    and the branching ratios to the SM final states are taken from
    \citep{Olive:2016xmw}. \ap{In this scenario, the LSP is assumed to be
    massless}.
    \Shufang{Specify M1 as well and use the actual Br.} \Adarsh{I added a line
  specifying that the LSP is massless. As for the actual BR, I assume you mean
  calculate it using SUSY-HIT? That'll take a bit more time, but I'll try to
  get it.}\Shufang{rewrite the entry.  Why chi2pm? Should not it be chi1pm?}}
  \Adarsh{$\chi_1$ is the LSP, right? In our case it's the bino, which is not
  charged...}
  \label{tab:xsections}
\end{table}

@@

In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production
cross section for the Higgsino-like NLSPs.  The cross section varies between
200 fb to 0.5 fb for Higgsino masses between 500 GeV and 2500 GeV. The right
panel of Fig.~\ref{fig:xsection_plot} shows the decay branching fractions of
$\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as calculated in SUSY-HIT \cite{Djouadi:2006bz}.
While one of the Higgsinos mostly decays to $Z$, the other
Higgsino mostly decays to $h$.  $Zh+\met$ signal thus provide an alternative
discovery channel for Higgsinos.

@@

Searches for pair produced nearly mass-degenerate Higgsinos  have been performed 
at ATLAS and CMS for various decay  topologies. While the identity of the 
LSP in these searches is a gravitino  instead of a Bino,   the limits are still  relevant, since both  our analysis  and the experimental ones consider that  
the neutral Higgsinos decay to a  neutral SM boson (\emph{h/Z})  and the 
LSP 100\% of the time.  \Shufang{But this is not the same as our Higgsino NLSP
and Bino LSP case.} \Adarsh{True, but there have been no experimental searches
for Higgsino NLSP - Bino LSP. This seemed like the most similar
channel/topology to ours.}

@@

  \item \emph{Razor variables}:  Two razor variables are used in our analyses: 
\begin{align}
M_R &=& \sqrt{(E_Z+E_h)^2 - (p_Z^z + p_h^z)^2},\\
M_T^R &=& \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)^2
- \vec{\slashed{E}}_T\cdot(\vec{p}_{ZT}+\vec{p}_{hT})\right]}
\end{align}
 for$E_{Z,h}$ and $p_{Z,h}$ being the reconstructed energy and momentum for $Z$ and $h$.
\Shufang{Check the formula.  Unit is not correct.}
    Representative kinematic
  distributions of these variables for signal events of a 1 TeV Higgsino and a 25 GeV Bino, as well as $tt$ and $tbW$ backgrounds are
  shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification, and
  $\slashed{E}_{T}$ cuts. The
  distribution for the \emph{bbWW} background is not shown, since it is negligible in
  comparison to the others.   We can see that the distribution of $M_R$ is peaked
  around 1 TeV for the signal, which consistent with what we would expect, since
  it corresponds to the mass difference between the NLSP and LSP.  For this mass combination, requiring $M_R >$ 800
  GeV and $M_T^R >$ 400 GeV yields the greatest significance.
